---
title: "Final Project"
output:
  word_document: default
  html_document:
    df_print: paged
  html_notebook: default
---
*Setting default values to get a clean output*
```{r}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

*Loading the required packages*
```{r}
library(lpSolve)
library(lpSolveAPI)
library(knitr)
library(dplyr)
```

**Reason for Choosing Accuracy, Analysis, Presentation**

**Accuracy:**

*Ensures correctness of information.*

*Avoids errors and misinformation.*

*Establishes reliability and trustworthiness.*

**Analysis:**

*Facilitates informed decision-making.*

*Adds depth and insight to the project.*

*Demonstrates critical thinking and expertise.*

**Presentation:**

*Enhances communication of ideas.*

*Improves readability and accessibility.*

*Reflects professionalism and credibility.*

**Data generation process:**

*Conducted a survey among 15 students to assess three key factors influencing group success—communication skills, time management, and leadership qualities.*

*Findings revealed insights into the perceived impact of Accuracy, Analysis, Presentation factors on group success, contributing to a comprehensive report with potential recommendations for enhancing group collaboration and effectiveness.*

*All three plays important role in total*

$$Total = (Accuracy + Analysis + Presentation)/3$$

*Loading the table of students along with the factors and their values*



```{r}
stu_table <- matrix(c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,
                  88,58,85,63,43,91,98,58,33,74,90,45,60,55,75,
                70,58,92,89,57,61,35,95,75,91,72,68,65,80,95,
                35,38,25,28,24,26,44,22,43,48,27,49,80,85,69,
            64,51,67,60,41,59,59,58,50,71,63,54,68,73,80),ncol = 5,byrow = F)

colnames(stu_table) <- c("Student","Accuracy","Analysis","Presentation","Total")

print(stu_table)
```

#### Objective Function:


### Constraints: 

*We can see that there are a total of 15 Students in this Class Group, who are going to work on a class project by combining into a group of 3 each.*


*The Three Factors that are used to assess a individual student's performance are "Accuracy" (1), "Analysis" (2), "Presentation" (3).*

*Accuracy, Analysis, and Presentation were weighed between 1 and 100 based on Survey.*

*Total is defined as weights of each of the factors for an individual student,*


$$F_{ij} \: where \: i= Students \: ranging \: from \:1-15 \: and \: ji \: the \: Factors \:ranging \: from \:1-3$$


##### Accuracy Constraints 

*There are total five constraints for Accuracy*

$$F1Group_1 = 88s_{1}g_{1}+58s_{2}g_{1}+85s_{3}g_{1}+63s_{4}g_{1}+43s_{5}g_{1}+91s_{6}g_{1}+98s_{7}g_{1}+58s_{8}g_{1}+33s_{9}g_{1}+74s_{10}g_{1}+90s_{11}g_{1}+45s_{12}g_{1}+60s_{13}g_{1}+55s_{14}g_{1}+75s_{15}g_{1} >= 68$$

$$F1Group_2 = 88s_{1}g_{2}+58s_{2}g_{2}+85s_{3}g_{2}+63s_{4}g_{2}+43s_{5}g_{2}+91s_{6}g_{2}+98s_{7}g_{2}+58s_{8}g_{2}+33s_{9}g_{2}+74s_{10}g_{2}+90s_{11}g_{2}+45s_{12}g_{2}+60s_{13}g_{2}+55s_{14}g_{2}+75s_{15}g_{2} >= 68$$

$$F1Group_3 = 88s_{1}g_{3}+58s_{2}g_{3}+85s_{3}g_{3}+63s_{4}g_{3}+43s_{5}g_{3}+91s_{6}g_{3}+98s_{7}g_{3}+58s_{8}g_{3}+33s_{9}g_{3}+74s_{10}g_{3}+90s_{11}g_{3}+45s_{12}g_{3}+60s_{13}g_{3}+55s_{14}g_{3}+75s_{15}g_{3} >= 68$$

$$F1Group_4 = 88s_{1}g_{4}+58s_{2}g_{4}+85s_{3}g_{4}+63s_{4}g_{4}+43s_{5}g_{4}+91s_{6}g_{4}+98s_{7}g_{4}+58s_{8}g_{4}+33s_{9}g_{4}+74s_{10}g_{4}+90s_{11}g_{4}+45s_{12}g_{4}+60s_{13}g_{4}+55s_{14}g_{4}+75s_{15}g_{4} >= 68$$


$$F1Group_5 = 88s_{1}g_{5}+58s_{2}g_{5}+85s_{3}g_{5}+63s_{4}g_{5}+43s_{5}g_{5}+91s_{6}g_{5}+98s_{7}g_{5}+58s_{8}g_{5}+33s_{9}g_{5}+74s_{10}g_{5}+90s_{11}g_{5}+45s_{12}g_{5}+60s_{13}g_{5}+55s_{14}g_{5}+75s_{15}g_{5} >= 68$$


##### Analysis Constraints

*There are total five constraints for Analysis*


$$F2Group_1 = 70s_{1}g_{1}+58s_{2}g_{1}+92s_{3}g_{1}+89s_{4}g_{1}+57s_{5}g_{1}+61s_{6}g_{1}+35s_{7}g_{1}+95s_{8}g_{1}+75s_{9}g_{1}+91s_{10}g_{1}+72s_{11}g_{1}+68s_{12}g_{1}+65s_{13}g_{1}+80s_{14}g_{1}+95s_{15}g_{1} >= 74$$

$$F2Group_2 = 70s_{1}g_{2}+58s_{2}g_{2}+92s_{3}g_{2}+89s_{4}g_{2}+57s_{5}g_{2}+61s_{6}g_{2}+35s_{7}g_{2}+95s_{8}g_{2}+75s_{9}g_{2}+91s_{10}g_{2}+72s_{11}g_{2}+68s_{12}g_{2}+65s_{13}g_{2}+80s_{14}g_{2}+95s_{15}g_{2} >= 74$$

$$F2Group_3 = 70s_{1}g_{3}+58s_{2}g_{3}+92s_{3}g_{3}+89s_{4}g_{3}+57s_{5}g_{3}+61s_{6}g_{3}+35s_{7}g_{3}+95s_{8}g_{3}+75s_{9}g_{3}+91s_{10}g_{3}+72s_{11}g_{3}+68s_{12}g_{3}+65s_{13}g_{3}+80s_{14}g_{3}+95s_{15}g_{3} >= 74$$

$$F2Group_4 = 70s_{1}g_{4}+58s_{2}g_{4}+92s_{3}g_{4}+89s_{4}g_{4}+57s_{5}g_{4}+61s_{6}g_{4}+35s_{7}g_{4}+95s_{8}g_{4}+75s_{9}g_{4}+91s_{10}g_{4}+72s_{11}g_{4}+68s_{12}g_{4}+65s_{13}g_{4}+80s_{14}g_{4}+95s_{15}g_{4} >= 74$$

$$F2Group_5 = 70s_{1}g_{5}+58s_{2}g_{5}+92s_{3}g_{5}+89s_{4}g_{5}+57s_{5}g_{5}+61s_{6}g_{5}+35s_{7}g_{5}+95s_{8}g_{5}+75s_{9}g_{5}+91s_{10}g_{5}+72s_{11}g_{5}+68s_{12}g_{5}+65s_{13}g_{5}+80s_{14}g_{5}+95s_{15}g_{5} >= 74$$

#### Presentation Constraints 

*There are total five constraints for Performance*


$$F3Group_1 = 35s_{1}g_{1}+38s_{2}g_{1}+25s_{3}g_{1}+28s_{4}g_{1}+24s_{5}g_{1}+26s_{6}g_{1}+44s_{7}g_{1}+22s_{8}g_{1}+43s_{9}g_{1}+48s_{10}g_{1}+27s_{11}g_{1}+49s_{12}g_{1}+80s_{13}g_{1}+85s_{14}g_{1}+69s_{15}g_{1} >= 43$$

$$F3Group_2= 35s_{1}g_{2}+38s_{2}g_{2}+25s_{3}g_{2}+28s_{4}g_{2}+24s_{5}g_{2}+26s_{6}g_{2}+44s_{7}g_{2}+22s_{8}g_{2}+43s_{9}g_{2}+48s_{10}g_{2}+27s_{11}g_{2}+49s_{12}g_{2}+80s_{13}g_{2}+85s_{14}g_{2}+69s_{15}g_{2} >= 43$$

$$F3Group_3 = 35s_{1}g_{3}+38s_{2}g_{3}+25s_{3}g_{3}+28s_{4}g_{3}+24s_{5}g_{3}+26s_{6}g_{3}+44s_{7}g_{3}+22s_{8}g_{3}+43s_{9}g_{3}+48s_{10}g_{3}+27s_{11}g_{3}+49s_{12}g_{3}+80s_{13}g_{3}+85s_{14}g_{3}+69s_{15}g_{3} >= 43$$

$$F3Group_4 = 35s_{1}g_{4}+38s_{2}g_{4}+25s_{3}g_{4}+28s_{4}g_{4}+24s_{5}g_{4}+26s_{6}g_{4}+44s_{7}g_{4}+22s_{8}g_{4}+43s_{9}g_{4}+48s_{10}g_{4}+27s_{11}g_{4}+49s_{12}g_{4}+80s_{13}g_{4}+85s_{14}g_{4}+69s_{15}g_{4} >= 43$$

$$F3Group_5 = 35s_{1}g_{5}+38s_{2}g_{5}+25s_{3}g_{5}+28s_{4}g_{5}+24s_{5}g_{5}+26s_{6}g_{5}+44s_{7}g_{5}+22s_{8}g_{5}+43s_{9}g_{5}+48s_{10}g_{5}+27s_{11}g_{5}+49s_{12}g_{5}+80s_{13}g_{5}+85s_{14}g_{5}+69s_{15}g_{5} >= 43$$

#### Student Constraints: 

*There are total twelve constraints for Students*


$$Student_{1}: s_{1}g_{1} + s_{1}g_{2} + s_{1}g_{3} + s_{1}g_{4} + s_{1}g_{5} = 1$$

$$Student_{2}: s_{2}g_{1} + s_{2}g_{2} + s_{2}g_{3} + s_{2}g_{4} + s_{2}g_{5} = 1$$
$$Student_{3}: s_{3}g_{1} + s_{3}g_{2} + s_{3}g_{3} + s_{3}g_{4} + s_{3}g_{5} = 1$$
$$Student_{4}: s_{4}g_{1} + s_{4}g_{2} + s_{4}g_{3} + s_{4}g_{4} + s_{4}g_{5} = 1$$
$$Student_{5}: s_{5}g_{1} + s_{5}g_{2} + s_{5}g_{3} + s_{5}g_{4} + s_{5}g_{5} = 1$$
$$Student_{6}: s_{6}g_{1} + s_{6}g_{2} + s_{6}g_{3} + s_{6}g_{4} + s_{6}g_{5} = 1$$
$$Student_{7}: s_{7}g_{1} + s_{7}g_{2} + s_{7}g_{3} + s_{7}g_{4} + s_{7}g_{5} = 1$$
$$Student_{8}: s_{8}g_{1} + s_{8}g_{2} + s_{8}g_{3} + s_{8}g_{4} + s_{8}g_{5} = 1$$
$$Student_{9}: s_{9}g_{1} + s_{9}g_{2} + s_{9}g_{3} + s_{9}g_{4} + s_{9}g_{5} = 1$$
$$Student_{10}: s_{10}g_{1} + s_{10}g_{2} + s_{10}g_{3} + s_{10}g_{4} + s_{10}g_{5} = 1$$
$$Student_{11}: s_{11}g_{1} + s_{11}g_{2} + s_{11}g_{3} + s_{11}g_{4} + s_{11}g_{5} = 1$$
$$Student_{12}: s_{12}g_{1} + s_{12}g_{2} + s_{12}g_{3} + s_{12}g_{4} + s_{12}g_{5} = 1$$
$$Student_{13}: s_{13}g_{1} + s_{13}g_{2} + s_{13}g_{3} + s_{13}g_{4} + s_{13}g_{5} = 1$$
$$Student_{14}: s_{14}g_{1} + s_{14}g_{2} + s_{14}g_{3} + s_{14}g_{4} + s_{14}g_{5} = 1$$
$$Student_{15}: s_{15}g_{1} + s_{15}g_{2} + s_{15}g_{3} + s_{15}g_{4} + s_{15}g_{5} = 1$$

#### Group Constraints

*There are total five constraints for Group*


$$Group_{1}: g_{1}s_{1} + g_{1}s_{2} + g_{1}s_{3} + g_{1}s_{4} + g_{1}s_{5} + g_{1}s_{6} + g_{1}s_{7} + g_{1}s_{8} + g_{1}s_{9} + g_{1}s_{10} + g_{1}s_{11} + g_{1}s_{12} + g_{1}s_{13} + g_{1}s_{14} + g_{1}s_{15} = 3 $$
$$Group_{2}: g_{2}s_{1} + g_{2}s_{2} + g_{2}s_{3} + g_{2}s_{4} + g_{2}s_{5} + g_{2}s_{6} + g_{2}s_{7} + g_{2}s_{8} + g_{2}s_{9} + g_{2}s_{10} + g_{2}s_{11} + g_{2}s_{12} + g_{2}s_{13} + g_{2}s_{14} + g_{2}s_{15} = 3 $$
$$Group_{3}: g_{3}s_{1} + g_{3}s_{2} + g_{3}s_{3} + g_{3}s_{4} + g_{3}s_{5} + g_{3}s_{6} + g_{3}s_{7} + g_{3}s_{8} + g_{3}s_{9} + g_{3}s_{10} + g_{3}s_{11} + g_{3}s_{12} + g_{3}s_{13} + g_{3}s_{14} + g_{3}s_{15} = 3 $$

$$Group_{4}: g_{4}s_{1} + g_{4}s_{2} + g_{4}s_{3} + g_{4}s_{4} + g_{4}s_{5} + g_{4}s_{6} + g_{4}s_{7} + g_{4}s_{8} + g_{4}s_{9} + g_{4}s_{10} + g_{4}s_{11} + g_{4}s_{12} + g_{4}s_{13} + g_{4}s_{14} + g_{4}s_{15} = 3 $$
$$Group_{5}: g_{5}s_{1} + g_{5}s_{2} + g_{5}s_{3} + g_{5}s_{4} + g_{5}s_{5} + g_{5}s_{6} + g_{5}s_{7} + g_{5}s_{8} + g_{5}s_{9} + g_{5}s_{10} + g_{5}s_{11} + g_{5}s_{12} + g_{5}s_{13} + g_{5}s_{14} + g_{5}s_{15} = 3 $$
### Non Negative Constraints

$$\sum_{i=1}^{15}s_i \sum_{j=1}^5g_i \ge 0, \:i=1-15,\: j=1-5$$

#### The Objective function is defined as

$Max: W_{ij}.X_{ij}$ where $W_{ij}$ is the weight of the factors to each student where $i=1-15$ and $j=1-3$ and $X_{ij}$ is the assignment of each student to a group where $i= Students$ ranging from $1-12$ and $jis$ the Groupsranging from $1-4$

$$MaxZ = 64s_{1}g_{1}+ 51s_{2}g_{1} + 67s_{3}g_{1} + 60s_{4}g_{1} + 41s_{5}g_{1} + 59s_{6}g_{1} + 59s_{7}g_{1} + 58s_{8}g_{1} + 50s_{9}g_{1} + 71s_{10}g_{1} + 63s_{11}g_{1} + 54s_{12}g_{1} + 68s_{13}g_{1} + 73S_{14}g_{1} + 80s_{15}g_{1} + 64s_{1}g_{2} + 51s_{2}g_{2} + 67s_{3}g_{2} + 60s_{4}g_{2} + 41s_{5}g_{2} + 59s_{6}g_{2} + 59s_{7}g_{2} + 58s_{8}g_{2} + 50s_{9}g_{2} + 71s_{10}g_{2} + 63s_{11}g_{2} + 54s_{12}g_{2} + 68s_{13}g_{2} + 73s_{14}g_{2} + 80s_{15}g_{2} +  64s_{1}g_{3} + 51s_{2}g_{3} + 67s_{3}g_{3} + 60s_{4}g_{3} + 41s_{5}g_{3} + 59s_{6}g_{3} + 59s_{7}g_{3} + 58s_{8}g_{3} + 50s_{9}g_{3} + 71s_{10}g_{3} + 63s_{11}g_{3} + 54s_{12}g_{3} + 68s_{13}g_{3} + 73s_{14}g_{3} + 80s_{15}g_{3} +  64s_{1}g_{4} + 51s_{2}g_{4} + 67s_{3}g_{4} + 60s_{4}g_{4} + 41s_{5}g_{4} + 59s_{6}g_{4} + 59s_{7}g_{4} + 58s_{8}g_{4} + 50s_{9}g_{4} + 71s_{10}g_{4} + 63s_{11}g_{4} + 54s_{12}g_{4} + 68s_{13}g_{4} + 73s_{14}g_{4} + 80s_{15}g_{4} +  64s_{1}g_{5} + 51s_{2}g_{5} + 67s_{3}g_{5} + 60s_{4}g_{5} + 41s_{5}g_{5} + 59s_{6}g_{5} + 59s_{7}g_{5} + 58s_{8}g_{5} + 50s_{9}g_{5} + 71s_{10}g_{5} + 63s_{11}g_{5} + 54s_{12}g_{5} + 68s_{13}g_{5} + 73s_{14}g_{5} + 80s_{15}g_{5}$$

### Solve Problem R Code

### Loading required libraries

```{r}

library(lpSolve)

library(lpSolveAPI)

```

*Solving the LP File*
```{r}
solveAP<-make.lp(35,75)

solveAP

```
*Since the solution function resulted as 0, this indicates that there exists a solution for this LP Formulation.*


*Getting the resultant objective function value*

```{r}

set.objfn(solveAP, c(64,51,67,60,41,59,59,58,50,71,63,54,68,73,80,
                     64,51,67,60,41,59,59,58,50,71,63,54,68,73,80,
                     64,51,67,60,41,59,59,58,50,71,63,54,68,73,80,
                     64,51,67,60,41,59,59,58,50,71,63,54,68,73,80,
                     64,51,67,60,41,59,59,58,50,71,63,54,68,73,80))

```


```{r}

lp.control(solveAP, sense = 'max')
```
### Set the constraints to the LP problem.

```{r}
set.row(solveAP,1,c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Group 1

set.row(solveAP,2,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Group 2

set.row(solveAP,3,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Group 3

set.row(solveAP,4,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Group 4

set.row(solveAP,5,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)) # Group 5


set.row(solveAP,6,c(88,58,85,63,43,91,98,58,33,74,90,45,60,55,75,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 1 as Analysis

set.row(solveAP,7,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,88,58,85,63,43,91,98,58,33,74,90,45,60,55,75,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 2 as Analysis

set.row(solveAP,8,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,88,58,85,63,43,91,98,58,33,74,90,45,60,55,75,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 3 as Analysis

set.row(solveAP,9,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,88,58,85,63,43,91,98,58,33,74,90,45,60,55,75,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 4 as Analysis

set.row(solveAP,10,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, 88,58,85,63,43,91,98,58,33,74,90,45,60,55,75)) # Factor 5 as Analysis


set.row(solveAP,11,c(70,58,92,89,57,61,35,95,75,91,72,68,65,80,95,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 1 as Accuracy

set.row(solveAP,12,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,70,58,92,89,57,61,35,95,75,91,72,68,65,80,95,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 2 as Accuracy

set.row(solveAP,13,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,70,58,92,89,57,61,35,95,75,91,72,68,65,80,95,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 3 as Accuracy

set.row(solveAP,14,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,70,58,92,89,57,61,35,95,75,91,72,68,65,80,95,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 4 as Accuracy

set.row(solveAP,15,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, 70,58,92,89,57,61,35,95,75,91,72,68,65,80,95)) # Factor 5 as Accuracy


set.row(solveAP,16,c(35,38,25,28,24,26,44,22,43,48,27,49,80,85,69,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 1 as Presentation

set.row(solveAP,17,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,35,38,25,28,24,26,44,22,43,48,27,49,80,85,69,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0
)) # Factor 2 as Presentation

set.row(solveAP,18,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,35,38,25,28,24,26,44,22,43,48,27,49,80,85,69,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 3 as Presentation

set.row(solveAP,19,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,35,38,25,28,24,26,44,22,43,48,27,49,80,85,69,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Factor 4 as Presentation

set.row(solveAP,20,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0, 35,38,25,28,24,26,44,22,43,48,27,49,80,85,69)) # Factor 5 as Presentation


set.row(solveAP,21,c(1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Student 1

set.row(solveAP,22,c(0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0)) # Student 2

set.row(solveAP,23,c(0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0)) # Student 3

set.row(solveAP,24,c(0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0)) # Student 4

set.row(solveAP,25,c(0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0)) # Student 5

set.row(solveAP,26,c(0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0)) # Student 6

set.row(solveAP,27,c(0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0)) # Student 7

set.row(solveAP,28,c(0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0)) # Student 8

set.row(solveAP,29,c(0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0)) # Student 9

set.row(solveAP,30,c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0)) # Student 10

set.row(solveAP,31,c(0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0)) # Student 11

set.row(solveAP,32,c(0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0)) # Student 12

set.row(solveAP,33,c(0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0)) # Student 13

set.row(solveAP,34,c(0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0))# Student 14

set.row(solveAP,35,c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,1)) # Student 15


```


### Setting the RHS values for the constraints in LP problem.

```{r}

rhs<-c(3,3,3,3,3,68,68,68,68,68,74,74,74,74,74,43,43,43,43,43,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

set.rhs(solveAP,rhs)

```

### Setting the directions(Types) and bounds to the LP problem.

```{r}

set.constr.type(solveAP,c("=","=","=","=","=",">=", ">=", ">=", ">=", ">=", ">=", ">=", ">=", ">=", ">=",">=", ">=", ">=", ">=", ">=","=","=","=","=","=","=","=","=","=","=","=","=","=","=","="))
set.bounds(solveAP,lower = rep(0,75))

```


### Convert the results into Interger
```{r}

set.type(solveAP, 1:75 ,type = c("integer")) 

solveAP

```

### Solving the Lp problem using the constraints and objective function.

```{r}

solve(solveAP)

```

### Getting the value of objective function.

```{r}

get.objective(solveAP)

```

### Getting the values of decision variables.

```{r}

var<- get.variables(solveAP)

var
```

### Getting the values of constraints.

```{r}

get.constraints(solveAP)

```

### FINDINGS

*Assigning students to different groups based on the constraints.*

*Students 13, 14, and 15 are in Group 1.*

*Students 1, 4, and 10 are in Group 2.*

*Students 3, 6, and 11 are in Group 3.*

*Students 2, 8, and 12 are in Group 4.*

*Students 5, 7, and 9 are in Group 15.*


