---
title: "BA64018_Assignment1"
author: "Ruthvick Bulagakula"
date: "2023-09-10"
output:
  pdf_document: default
  html_document: default
KSU ID: '811221623'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem 1

1. Back Savers is a company that produces backpacks primarily for students. They are
considering offering some combination of two different models—the Collegiate and the
Mini. Both are made out of the same rip-resistant nylon fabric. Back Savers has a long-
term contract with a supplier of the nylon and receives a 5000 square-foot shipment of
the material each week. Each Collegiate requires 3 square feet while each Mini requires 2
square feet. The sales forecasts indicate that at most 1000 Collegiates and 1200 Minis can
be sold per week. Each Collegiate requires 45 minutes of labor to produce and generates
a unit profit of $32. Each Mini requires 40 minutes of labor and generates a unit profit of
$24. Back Savers has 35 laborers that each provides 40 hours of labor per week.
Management wishes to know what quantity of each type of backpack to produce per
week.

    a. Clearly define the decision variables
    b. What is the objective function?
    c. What are the constraints?
    d. Write down the full mathematical formulation for this LP problem.
    
### LP Model for Problem 1

This represents data in the table format.

```{r}
data = matrix(c(3,1000,45, '$32',
                2,1200,40,'$24'), ncol=4, byrow = TRUE)

colnames(data) = c('Square-Feet', 'Sales', 'Time', 'Profit')
rownames(data) = c('Collegiate', 'Mini')

final = as.table(data)

print(final)

```
**Decision Variable**

Let us assume, $x_c$ for number of collegiate and $x_m$ for number of mini.

**Objective Function**

Objective for back savers is to increase profits. So, collegiate is making $32$ Dollars profit and mini is making $24$ Dollars profit.

Objective function for Back savers: $Z = 32x_c + 24x_m$

**Constraints**

***Material Constraint:***

Total square foot nylon material used for production cannot exceed $5000$ square feet. So, this can be expressed as $3x_c + 2x_m  <= 5000$

***Sales Constraint:***

Sales forecasts indicate that $1000$ collegiatee backpacks and $1200$ mini backpacks can be sold per week. So, this can be expressed as $x_c <= 1000$ , $x_m <= 1200$

***Labor Constraint:***

Back savers has $35$ labors and they work $40$ hours per week each. Each collegiate need $45$ mins of labor and each mini need $40$ mins of labor. So, this can be expressed in hours by dividing mins by $60$ since we have hours included as $40$ per week. 

$0.75x_c + 0.67x_m <= 35*40$

$0.75x_c + 0.67x_m <= 1400$

***Non Negative Constraint:***

$x_c>=0$ , $x_m>=0$

    
### Problem 2

2. The Weigelt Corporation has three branch plants with excess production capacity.
Fortunately, the corporation has a new product ready to begin production, and all three
plants have this capability, so some of the excess capacity can be used in this way. This
product can be made in three sizes--large, medium, and small--that yield a net unit profit
of $420, $360, and $300, respectively. Plants 1, 2, and 3 have the excess capacity to
produce 750, 900, and 450 units per day of this product, respectively, regardless of the
size or combination of sizes involved.
The amount of available in-process storage space also imposes a limitation on the
production rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000
square feet, respectively, of in-process storage space available for a day's production of
this product. Each unit of the large, medium, and small sizes produced per day requires
20, 15, and 12 square feet, respectively.
Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large,
medium, and small sizes, respectively, would be sold per day.
At each plant, some employees will need to be laid off unless most of the plant’s
excess production capacity can be used to produce the new product. To avoid layoffs if
possible, management has decided that the plants should use the same percentage of their
excess capacity to produce the new product.
Management wishes to know how much of each of the sizes should be produced
by each of the plants to maximize profit.

     a. Define the decision variables
     b. Formulate a linear programming model for this problem.
     
### LP Model for Problem 2

This represents data in the table format.

```{r}
data_plant = matrix(c(750,13000,
                900,12000,
                450,5000), ncol=2, byrow = TRUE)

colnames(data_plant) = c('Capacity', 'Square Feet')
rownames(data_plant) = c('P1', 'P2', 'P3')

final_plant = as.table(data_plant)

print(final_plant)

data_size = matrix(c(20,900,'$420',
                      15,1200,'360',
                      12,750,'$900'), ncol=3, byrow = TRUE)

colnames(data_size) = c('Square Feet', 'Sales', 'Profit')
rownames(data_size) = c('Large', 'Medium', 'Small')

final_size = as.table(data_size)

print(final_size)

```

**Decision Variable**

Let us assume, $p1_l$ , $p1_m$ , $p1_s$ for plant 1, $p2_l$ , $p2_m$ , $p2_s$ for plant 2, and $p3_l$ , $p3_m$ , $p3_s$ for plant 3.

**Objective Function**

Objective for Weigelt Corporation is to increase profits. So, all large units in all plants are making $420$ Dollars profit, all medium units in all plants are making $360$ Dollars profit, and all small units in all plants are making $300$ Dollars profit

Objective function for Weigelt Corporation: $Z = 420(p1_l+p2_l+p3_l)+ 360(p1_m+p2_m+p2_m)+ 300(p1_s+p2_s+p3_s)$

**Constraints**

***Capacity Constraint:***

Total units produced by plant 1 per week is $750$, Total units produced by plant 1 per week is $900$, and Total units produced by plant 1 per week is $450$.

Plant 1: $p1_l + p1_m + p1_s <= 750$

Plant 2: $p2_l + p2_m + p2_s <= 900$

Plant 3: $p3_l + p3_m + p3_s <= 450$

***Storage Constraint:***

Total square feet required for large per week is $20$, Total square feet required for medium per week is $15$, and Total square feet required for small per week is $12$

Total square feet required for plant 1 is $13000$, Total square feet required for plant 2 is $12000$, and Total square feet required for plant 3 is $5000$

Plant 1: $20p1_l + 15p1_m + 12p1_s <= 13000$

Plant 2: $20p2_l + 15p2_m + 12p2_s <= 12000$

Plant 3: $20p3_l + 15p3_m + 12p3_s <= 5000$

***Same Capaticy Constraint:***

To ensure same percentage of excess capacity does not exceed at each plant. So, we can use constraint like this 

$p1_l + p1_m + p1_s/750 = p2_l + p2_m + p2_s/900 = p3_l + p3_m + p3_s/450$

***Non Negative Constraint:***

$p1_l , p1_m , p1_s , p2_l , p2_m , p2_s , p3_l , p3_m , p3_s >= 0$

