---
title: "BA64018_Assignment2"
author: "Ruthvick Bulagakula"
date: "2023-09-24"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem 

The Weigelt Corporation has three branch plants with excess production capacity.
Fortunately, the corporation has a new product ready to begin production, and all three
plants have this capability, so some of the excess capacity can be used in this way. This
product can be made in three sizes--large, medium, and small--that yield a net unit profit
of $420, $360, and $300, respectively. Plants 1, 2, and 3 have the excess capacity to
produce 750, 900, and 450 units per day of this product, respectively, regardless of the
size or combination of sizes involved.
The amount of available in-process storage space also imposes a limitation on the
production rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000
square feet, respectively, of in-process storage space available for a day's production of
this product. Each unit of the large, medium, and small sizes produced per day requires
20, 15, and 12 square feet, respectively.
Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large,
medium, and small sizes, respectively, would be sold per day.
At each plant, some employees will need to be laid off unless most of the plant’s
excess production capacity can be used to produce the new product. To avoid layoffs if
possible, management has decided that the plants should use the same percentage of their
excess capacity to produce the new product.
Management wishes to know how much of each of the sizes should be produced
by each of the plants to maximize profit.

Solve the problem using lpsolve, or any other equivalent library in R.


### LP Model 

This represents data in the table format.

```{r}
data_plant = matrix(c(750,13000,
                900,12000,
                450,5000), ncol=2, byrow = TRUE)

colnames(data_plant) = c('Capacity', 'Square Feet')
rownames(data_plant) = c('P1', 'P2', 'P3')

final_plant = as.table(data_plant)

print(final_plant)

data_size = matrix(c(20,900,'$420',
                      15,1200,'360',
                      12,750,'$900'), ncol=3, byrow = TRUE)

colnames(data_size) = c('Square Feet', 'Sales', 'Profit')
rownames(data_size) = c('Large', 'Medium', 'Small')

final_size = as.table(data_size)

print(final_size)

```

**Decision Variable**

Let us assume, $p1_l$ , $p1_m$ , $p1_s$ for plant 1, $p2_l$ , $p2_m$ , $p2_s$ for plant 2, and $p3_l$ , $p3_m$ , $p3_s$ for plant 3.

**Objective Function**

Objective for Weigelt Corporation is to increase profits. So, all large units in all plants are making $420$ Dollars profit, all medium units in all plants are making $360$ Dollars profit, and all small units in all plants are making $300$ Dollars profit

Objective function for Weigelt Corporation: 

$Z = 420(p1_l+p2_l+p3_l)+ 360(p1_m+p2_m+p3_m)+ 300(p1_s+p2_s+p3_s)$

**Constraints**

***Capacity Constraint:***

Total units produced by plant 1 per week is $750$, Total units produced by plant 1 per week is $900$, and Total units produced by plant 1 per week is $450$.

Plant 1: $p1_l + p1_m + p1_s <= 750$

Plant 2: $p2_l + p2_m + p2_s <= 900$

Plant 3: $p3_l + p3_m + p3_s <= 450$

***Storage Constraint:***

Total square feet required for large per week is $20$, Total square feet required for medium per week is $15$, and Total square feet required for small per week is $12$

Total square feet required for plant 1 is $13000$, Total square feet required for plant 2 is $12000$, and Total square feet required for plant 3 is $5000$

Plant 1: $20p1_l + 15p1_m + 12p1_s <= 13000$

Plant 2: $20p2_l + 15p2_m + 12p2_s <= 12000$

Plant 3: $20p3_l + 15p3_m + 12p3_s <= 5000$

***Salesforecast Capacity***

Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large,
medium, and small sizes, respectively, would be sold per day.

$p1_l + p2_l + p3_l <= 900$

$p1_m + p2_m + p3_m <= 1200$

$p1_s + p2_s + p3_s <= 750$

***Same Capaticy Constraint:***

To ensure same percentage of excess capacity does not exceed at each plant. So, we can use constraint like this 

$p1_l + p1_m + p1_s/750 = p2_2 + p2_m + p2_s/900 = p3_3 + p3_m + p3_s/450$

$900(p1_l + p1_m + p1_s) - 750(p2_2 + p2_m + p2_s) = 0$

$450(p2_2 + p2_m + p2_s) - 900(p3_3 + p3_m + p3_s) = 0$

$450(p3_3 + p3_m + p3_s) - 750(p1_l + p1_m + p1_s) = 0$

***Non Negative Constraint:***

$p1_l , p1_m , p1_s , p2_l , p2_m , p2_s , p3_l , p3_m , p3_s >= 0$

**Mathematical Formula**

Decision Variable: 

$p1_l$ , $p1_m$ , $p1_s$ , $p2_l$ , $p2_m$ , $p2_s$ , $p3_l$ , $p3_m$ , $p3_s$ 

Objective Function: 

$Z = 420(p1_l+p2_l+p3_l)+ 360(p1_m+p2_m+p3_m)+ 300(p1_s+p2_s+p3_s)$

Constraints:

Capacity Constraint: 

Plant 1: $p1_l + p1_m + p1_s <= 750$

Plant 2: $p2_l + p2_m + p2_s <= 900$

Plant 3: $p3_l + p3_m + p3_s <= 450$

Storage Capacity: 

Plant 1: $20p1_l + 15p1_m + 12p1_s <= 13000$

Plant 2: $20p2_l + 15p2_m + 12p2_s <= 12000$

Plant 3: $20p3_l + 15p3_m + 12p3_s <= 5000$

Salesforecast Capacity:

$p1_l + p2_l + p3_l <= 900$

$p1_m + p2_m + p3_m <= 1200$

$p1_s + p2_s + p3_s <= 750$

Same Capacity Constraint:

$p1_l + p1_m + p1_s/750 = p2_2 + p2_m + p2_s/900 = p3_3 + p3_m + p3_s/450$

$900(p1_l + p1_m + p1_s) - 750(p2_2 + p2_m + p2_s) = 0$

$450(p2_2 + p2_m + p2_s) - 900(p3_3 + p3_m + p3_s) = 0$

$450(p3_3 + p3_m + p3_s) - 750(p1_l + p1_m + p1_s) = 0$

Non Negative Constraint: 

$p1_l , p1_m , p1_s , p2_l , p2_m , p2_s , p3_l , p3_m , p3_s >= 0$

So, this above mathematical formulas will help Weigelt Corporation to maximize profits.


### Solution in R

**Calling Installed Library***
```{r}

library(lpSolve)

```
**Defining Objective Function**

```{r}

MaxZ = c(420,360,300,420,360,300,420,360,300)

```
**Defining Constraints**

```{r}

constraints = matrix(c(1,1,1,0,0,0,0,0,0,
                 0,0,0,1,1,1,0,0,0,
                 0,0,0,0,0,0,1,1,1,
                 20,15,12,0,0,0,0,0,0,
                 0,0,0,20,15,12,0,0,0,
                 0,0,0,0,0,0,20,15,12,
                 1,0,0,1,0,0,1,0,0,
                 0,1,0,0,1,0,0,1,0,
                 0,0,1,0,0,1,0,0,1,
                 900,900,900,-750,-750,-750,0,0,0,
                 0,0,0,450,450,450,-900,-900,-900,
                 450,450,450,0,0,0,-750,-750,-750), ncol = 9, byrow = TRUE)

```
**Defining Signs used for constraints**
```{r}

signs = c("<=","<=","<=","<=","<=","<=", "<=","<=","<=","=","=","=")

```
**Defining Sign values used for constraints**

```{r}

sign_values = c(750,900,450,13000,12000,5000,900,1200,750,0,0,0)

```

**Objective Function**

```{r}

lp_result = lp("max", MaxZ, constraints, signs, sign_values)

print(lp_result)

```
**LP Model Solution**

```{r}

lp_result$solution

```

